---
title: "CombiningTables"
author: "Komolafe Oyindolapo"
date: "2019 M08 12"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is the solution to Comprehensive check.

<strong>Question 1:</strong> You have created data frames tab1 and tab2 of state population and election data, similar to our module videos:
<pre><code>> tab1
state   	     population
Alabama             4779736
Alaska     	         710231
Arizona    	        6392017
Delaware     	     897934
District of Columbia 601723

> tab2
state  electoral_votes
Alabama      9
Alaska       3
Arizona     11
California  55
Colorado     9
Connecticut  7

> dim(tab1)
[1] 5 2

> dim(tab2)
[1] 6 2 </code></pre>
What are the dimensions of the table dat, created by the following command?

<pre><code>dat <- left_join(tab1, tab2, by = “state”)</pre></code>

<strong>Answer:</strong><code> 5 rows by 3 columns correct </code>

<strong>Question 2:</strong> We are still using the <code> tab1 </code> and <code> tab2 </code> tables shown in question 1. What join command would create a new table “dat” with three rows and two columns?

<p><strong>Answer:</strong> <code>dat <- semi_join(tab1, tab2, by = “state”) </code></p>


<strong>Question3</strong> Which of the following are real differences between the join and bind functions?
<strong>Answer:</strong><pre><code>
- Binding functions combine by position, while join functions match by variables.
- Joining functions can join datasets of different dimensions, but the bind functions must match on the appropriate dimension (either same row or column numbers).
- Bind functions can combine both vectors and dataframes, while join functions work for only for dataframes.
</code></pre>



```{r message=FALSE, warning=FALSE}


```