---
title: "WebScraping"
author: "Komolafe Oyindolapo"
date: "2019 M08 13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 4

Create a table called <code>tab_1</code> using entry 10 of nodes. Create a table called <code>tab_2</code> using entry 19 of nodes.

Note that the column names should be <code>c("Team", "Payroll", "Average")</code>. You can see that these column names are actually in the first data row of each table, and that tab_1 has an extra first column No. that should be removed so that the column names for both tables match.

Remove the extra column in tab_1, remove the first row of each dataset, and change the column names for each table to <code> c("Team", "Payroll", "Average") </code>. Use a full_join by the Team to combine these two tables.

How many rows are in the joined data table?

```{r warning=FALSE, message=FALSE}
library(rvest)
library(tidyverse)
url <- "https://web.archive.org/web/20181024132313/http://www.stevetheump.com/Payrolls.htm"
h <- read_html(url)
nodes <- html_nodes(h, "table")
tab_1 <- html_table(nodes[[10]])
tab_2 <- html_table(nodes[[19]])
tab_1 <- tab_1[-1]
tab_1 <- tab_1 %>% slice(2:n())%>% setNames(c(X2 ="Team", X3 = "Payroll", X4 = "Average"))

tab_2 <- tab_2 %>% slice(2:n())%>% setNames(c(X2 ="Team", X3 = "Payroll", X4 = "Average"))

dat_full <- full_join(tab_1, tab_2, by = "Team")
dat_full
```

## Question 5
<pre><code>
library(rvest)
library(tidyverse)
url <- "https://en.wikipedia.org/w/index.php?title=Opinion_polling_for_the_United_Kingdom_European_Union_membership_referendum&oldid=896735054"
</code></pre>
Assign tab to be the html nodes of the "table" class.

How many tables are in this Wikipedia page?
```{r}
url_1 <- "https://en.wikipedia.org/w/index.php?title=Opinion_polling_for_the_United_Kingdom_European_Union_membership_referendum&oldid=896735054"
h_1 <- read_html(url_1)
tab <- html_nodes(h_1, "table")
read <- html_table(tab[[7]], fill = TRUE)
```


